---
title: "Removing Internal Elements"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Removing Internal Elements}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shredder)
library(butcher)
library(details)
```

`stanfit` object hold a lot of information and some of the elements that take of most of the memory are not necessarily needed in post-processing. This vignette introduces verbs that can safely remove these elements without corrupting the stanfit object.

```{r,results='hide',message=FALSE}
rats <- rats_example(nCores = 1)

```
 
```{details, details.summary = 'The Model'}
rats@stanmodel
```

```{details, details.summary = 'Model Summary'}
rats
```

We use the [butcher](https://tidymodels.github.io/butcher/) package to evaluate the size of each element.

```{r}

rats%>%
  attributes()%>%
  butcher::weigh(units = 'MB')

```
 
## stan_axe

`shredder` can remove three elements in the `stanfit` object 

  - The cached fit summary stored in fit@`.MISC`$summary
  - The cached cpp object stored in fit@.MISC$stan_fit_instance
  - The stanmodel stored in fit@stanmodel
 
```{r}

summary <- function(x){
  
    y <- x%>%
    attributes()%>%
    butcher::weigh()
    
    s <- y$size
    
    data.frame(min = min(s),
               max = max(s),
               mean = mean(s), 
               sd = sd(s), 
               sum = sum(s))
    
  }
```

```{r}
butcher_rats <- rats%>%
  summary()

butcher_fit_instance <- rats%>%
  stan_axe(what = 'fit_instance')%>%
  summary()

butcher_stanmodel <- rats%>%
  stan_axe(what = 'fit_instance')%>%
  stan_axe(what = 'stanmodel')%>%
  summary()

butcher_summary <- rats%>%
  stan_axe(what = 'fit_instance')%>%
  stan_axe(what = 'stanmodel')%>%
  stan_axe(what = 'summary')%>%
  summary()

butcher_params <- rats%>%
  stan_axe(what = 'fit_instance')%>%
  stan_axe(what = 'stanmodel')%>%
  stan_axe(what = 'summary')%>%
  stan_select(alpha)%>%
  summary()

```
  
## Compare Object Sizes 
 
```{r}
tbl <- purrr::map_df(
  list('full' = butcher_rats,
       'fit_instance' = butcher_fit_instance,
       'stanmodel' = butcher_stanmodel,
       'summary' = butcher_summary,
       'param' = butcher_params),
  identity,.id='axe')
```
 
```{r}
knitr::kable(tbl) 
```