---
title: "Working with rstan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
stopifnot(require(knitr))
options(width = 90)
opts_chunk$set(
  comment = NA,
  message = FALSE,
  warning = FALSE,
  eval = TRUE,
  dev = "png",
  dpi = 150,
  fig.asp = 0.8,
  fig.width = 5,
  out.width = "60%",
  fig.align = "center"
)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(shredder)
library(rstan)
```

```{r,results='hide',warning=FALSE,message=FALSE}
rats <- shredder::rats_example(nCores = 1)
```

```{r,eval = FALSE}
rats
```

```{r,echo = FALSE}
rats%>%
  details::details(summary = 'Standard Output')
```

```{r,echo=FALSE}
details::details(system.file('rats.stan',package='shredder'),
                 summary = 'The Stan Script',lang = 'c')
```


## Pars

### Names

```{r}
rats%>%
  stan_names()

rats%>%
  stan_names(expand = TRUE)
```

### Select

```{r}
rats%>%
  stan_select(mu_alpha)

rats%>%
  stan_select(mu_alpha,mu_beta)

rats%>%
  stan_select(!!!rlang::syms(c('mu_alpha','mu_beta')))


rats%>%
  stan_select(alpha[1],alpha[2])


rats%>%
  stan_select(!!!rlang::syms(sprintf('alpha[%s]',1:5)))

```

### Select with Partials


```{r,eval=FALSE}
rats%>%
  stan_select(stan_contains('alpha'))

```

```{r,echo = FALSE}
rats%>%
  stan_select(stan_contains('alpha'))%>%
  details::details(summary = 'Select all Parameters that contain "alpha"')

```

```{r}
rats%>%
  stan_select(stan_contains('alpha\\[1\\]'))

rats%>%
  stan_select(stan_contains('alpha\\[[1-9]\\]'))

rats%>%
  stan_select(stan_ends_with('0'))

rats%>%
  stan_select(mu_alpha,stan_ends_with('0'),beta[1])
```

## Post-warmup samples

### Subsetting post warmup samples

```{r,eval=FALSE}

  rats%>%
    stan_slice(1:50,inc_warmup = TRUE)

```

```{r,echo=FALSE}

  rats%>%
    stan_slice(1:50,inc_warmup = TRUE)%>%
  details::details(summary = 'First 50 with warmup samples')

```

```{r,eval=FALSE}
  rats%>%
    stan_slice(1:50,inc_warmup = FALSE)

```


```{r,echo=FALSE}
  rats%>%
    stan_slice(1:50,inc_warmup = FALSE)%>%
  details::details(summary = 'First 50 draws from each chain <em>without</em> warmup samples')

```

```{r,eval=FALSE}
  rats%>%
    stan_sample_n(100)

```

```{r,echo=FALSE}
  rats%>%
    stan_sample_n(100)%>%
  details::details(summary = 'Sample 100 draws from each Chain')

```

```{r,eval=FALSE}

  rats%>%
    stan_sample_frac(0.5)

```

```{r,echo=FALSE}
rats%>%
    stan_sample_frac(0.5)%>%
    details::details(summary = 'Sample 50% of the Samples From each Chain')

```

### Select and Slice

```{r}
rats%>%
    stan_select(mu_alpha)%>%
    stan_slice(1:50)

```

### Retain Chains

```{r}
rats%>%
   stan_retain(chains = 1)
   
rats%>%
   stan_retain(chains = c(1,3))
```


### Filter

Users can filter conditionally on posterior samples. The function will locate the indicies that the logical expression returns for each chain. Due to a constraint in `rstan::extract` with `permuted=FALSE` chains are assumed to be of equal size. To keep this assumption the chain size returned is the length of the shortest conditional chain. If there is a chain that results in no samples then the chain is dropped with a warning. If no elements are returned for any chain then `NULL` is returned.

```{r}
rats%>%
   stan_select(mu_alpha,mu_beta)%>%
   stan_filter(mu_beta < 6)
 
```
